Parallel global optimization algorithm with uniform convergence for solving a set of constrained global optimization problems\thanks{This study was supported by the Russian Science Foundation, project No.\,16-11-10150.}

### 2020-10-02 2020/OPTIMA/Answers.tex
OPTIMA: add revised versions of the answers and paper

We thank very much all the reviewers for their useful comments and suggestions.
Please find below our answers that we suggest to clarify the issues.

@@

\textbf{Answer}.
The paper corrected by an English-speaking person.

@@

@@

\textbf{Answer}.
В рассматриваемых задачах целевая функция и ограничения предполагаются многоэкстремальными и заданными в виде ``черного ящика''. Кроме того, подразумевается, что каждое испытание (т.е. последовательное вычисление значений ограничений и целевой фукнции) является трудоемкой операцией и может потребовать значительных вычислительных ресурсов. Такая постановка часто встречается при решении прикладных задач (например, задач нелинейной аппроксимации; решении систем нелинейных уравнений и неравенств; подборе параметров математических моделей по экспериментальным данным, и т.п.). Поэтому задачи липшицевой глобальной оптимизации даже с одной переменной до сих пор вызывают интерес исследователей [1,2], а задачи размерности 2-3 являются стандартными для тестирования и сравнения алгоритмов липшицевой глобальной оптимизации [3].

В статью добавлен комментарий по поводу сложности задач рассматриваемого класса (see ...), а также численные эксперименты
по решению задач размерности 4 (see Section 4.1 and Table 1).

@@

\textbf{Answer}.
Результаты сравнения core Global Search Algorithm с рядом nature-inspired methods при решении нескольких сотен тестовых задач приведены в [1]. Результаты показывают, что GSA обеспечивает лучшее качество решения задач (решается большее число задач за меньшее число поисковых испытаний). В текст статьи добавлен соответствующий комментарий (see page ...).

Еще раз отметим, что в работе рассматриваются задачи с функциями вида ``черный ящик'' (i.e., an analytical representation of the functions is not available). Поэтому сравнение с методами, использующими аналитическое представление функций задачи (например, основанными на идеях DC-оптимизации, see [2] and references given therein) не будет являться корректным. В текст статьи добавлен соответствующий комментарий (see page ...).

@@

\begin{enumerate}
\item p. 3. Apparently, $z_k\neq g_s(x_k ) =:z_{ks}$.
\textbf{Answer}.
This formula was reformulated.

@@

\textbf{Answer}.
Definitions and terminology in the Section 3 was corrected.

@@

@@

>>>>

We would like to express our deepest gratitute to all the reviewers for their useful comments and suggestions.
Please find below our answers and clarifications of the issues.

@@

\textbf{Answer}.
The paper was reviewed and corrected by an experienced translator. Some parts of the text were reformulated or rewritten to improve readability and correct grammatical mistakes.

@@

\textbf{Answer}.
Clarification of the objective of this work was added at the end of Section 2.

@@

\textbf{Answer}.
The target function and constraints in the considered tasks are assumed to be multiextreme and set as a "black box". In addition, we assumed that each trial (i.e. sequential calculation of constraints and target function values) is a labor-intensive operation and may require significant computational resources. Such setting is often encountered in solving applied problems (e.g., problems of nonlinear approximation; solving systems of nonlinear equations and inequalities; selecting parameters of mathematical models from experimental data, etc.). Therefore, even the problems of Lipschitz global optimization with only one variable still remain of interest to researchers [1,2], and problems of higher dimensionality (2-3) are considered standard for tests and comparison of algorithms of Lipschitz  global optimization [3].

We added a comment on the complexity of the considered class of problems (see ...), as well as numerical experiments on solving dimensionality problems 4 (see Section 4.1 and Table 1).

@@

\textbf{Answer}.
The results of comparison of core Global Search Algorithm with a number of nature-inspired methods when solving several hundred test tasks are given in [1]. The results show that GSA provides better quality of problem solving (more problems are solved in fewer search trials). A corresponding comment has been added to the manuscript (see page 11).

Once again, we would like to point out that the article considers problems with "black box" functions (i.e., an analytical representation of the functions is not available). Therefore, comparing them with methods based on analytical representation of the task functions (for example, based on the ideas of DC-optimization, see [2] and references given therein) would not be appropriate. An relevant comment has been added to the manuscript (see page 2).

@@

\begin{enumerate}
\item p. 3. Apparently, $z_k\neq g_s(x_k ) =:z_{ks}$.
\textbf{Answer}.
This formula was rewritten.

@@

\textbf{Answer}.
Definitions and terminology in the Section 3 were corrected.

@@

\textbf{Answer}.
The presented method converges to all the global optimal solutions at once, but numerically it's hard
to obtain them all with a guarentee. That happens due to lack of an appropriate stopping criterion.

@@

A series of global optimization problems can arise from an mixed-integer problem or
after scalarization [1] of an multi-objective problem [2]. In both cases, all the problems from the series have to be solved with approximately similar quality, because all of
them are equally important. To speedup this process under constrained computational resources,
we can apply parallel computations along with a resource balancing approach to guarantee equal
quality of solutions in all the problems by the end of the optimization process.

1. Barkalov, K. and I. Lebedev. “Parallel Global Optimization for Non-convex Mixed-Integer Problems.” RuSCDays (2019).

2. Jahn J. Scalarization in Multi Objective Optimization. In: Serafini P. (eds) Mathematics of Multi Objective Optimization. International Centre for Mechanical Sciences (Courses and Lectures), vol 289. Springer, Vienna (1985).
